Maximum Entropy Spectral Analysis: a case study

### 2021-03-25 paper/mesa.tex
Tiny change

We perform two sets of experiments.
In the first one (see fig.~\ref{fig:mem_welch_fakedata}), we simulate data from an analytical PSD and we make the comparison with them: this is to ensure the we have a baseline PSD to compare the data with.
In a second experiment (see fig.~\ref{fig:mem_welch_realdata}), we employ the data released to the public by the LIGO/Virgo collaboration \cite{Abbott_2021}.
In each experiment, we vary the length of the data used for the estimation: this is also useful to assess how the computation depends on the data available. We set the total observation time $T = 1, 5, 10, 100, 1000 \SI{}{s}$
For the MESA algorithm, we employ FPE optimizer. For the Welch algorithm, we employ a Tukey window, an overlap fraction of $0.5$ for the segments and a length of segments $L = 512, 1024, 2048, 8192, 32768$ datapoints.
In all cases, the sampling rate is set to $\SI{4096}{Hz}$.

@@

\begin{figure}
	\label{fig:mem_welch_fakedata}
	\caption{Make here a comparison between Welch - Fake data}
	\includegraphics{Images/comparison_LVC_data/comparison_LVC_data_overall_fake_True.pdf}
\end{figure}
\begin{figure}
	\label{fig:mem_welch_realdata}
	\caption{Make here a comparison between Welch - True data}
	\includegraphics{Images/comparison_LVC_data/comparison_LVC_data_overall_fake_False.pdf}
\end{figure}

\sschmidt{Mettiamo da qualche parte una descrizione dettagliata del codice? No: solo rimandiamo al codice nell'intro}

@@

	\begin{acknowledgments}
\sschimidt{Is it fine to ackonowledge people helping with temperature data and seismic data?}
%S.S. wants to thank Maurizio Maugeri and Costanza Rossi for useful discussions.

>>>>

We perform two sets of experiments.
In the first one (see fig.~\ref{fig:mem_welch_fakedata}), we simulate data from the realesed LIGO intererferometer PSD and we make the comparison with them: this is to ensure the we have a baseline PSD to compare the data with.
In a second experiment (see fig.~\ref{fig:mem_welch_realdata}), we employ the data released to the public by the LIGO/Virgo collaboration \cite{Abbott_2021}.
In each experiment, we vary the length of the data used for the estimation: this is also useful to assess how the computation depends on the data available. We set the total observation time $T = 1, 5, 10, 100, 1000 \SI{}{s}$
For the MESA algorithm, we employ FPE optimizer. For the Welch algorithm, we employ a Tukey window, an overlap fraction of $0.5$ for the segments and a length of segments $L = 512, 1024, 2048, 8192, 32768$ datapoints.
In all cases, the sampling rate is set to $\SI{4096}{Hz}$.

@@

\begin{figure}
	\caption{Make here a comparison between Welch - Fake data}
	\label{fig:mem_welch_fakedata}
	\includegraphics{Images/comparison_LVC_data/comparison_LVC_data_overall_fake_True.pdf}
\end{figure}

\begin{figure}
	\caption{Make here a comparison between Welch - True data}
	\label{fig:mem_welch_realdata}
	\includegraphics{Images/comparison_LVC_data/comparison_LVC_data_overall_fake_False.pdf}
\end{figure}

@@

\sschimidt{Is it fine to ackonowledge people helping with temperature data and seismic data?}
	\begin{acknowledgments}
%S.S. wants to thank Maurizio Maugeri and Costanza Rossi for useful discussions.
